\LARGE \bf Efficient Planar Sample-Based Grasp Planning with Uncertainty Using Budgeted Multi-Armed Bandit Models for [v3 Jan 5, 2015 ]

### 2015-01-05 paper.tex
v3 after Ken's Feedback

\title{\LARGE \bf
Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v2] }

@@

\begin{abstract}
\textit{Note to Practitioners---}Planning for a grasp in an unknown environment can be difficult due to ucertainities. For example, a given object may have transparency which makes modern kinect-like sensor unable to accurately determine shape or an object may have a built up of mildew or dust, which makes the friction coefficient unknown. To handle all the uncertainites and plan for grasps using a grasp metric, one must perform monte-carlo integration and exhaustively evaluate samples. We show that by using simple algorithms from the Multi-Armed bandit literature, you can intelligently decided which grasp to sample from next and quickly determine the best grasp in a given set of proposed grasps. 
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Consider a robot packing boxes in a shipping warehouse environment, where it may frequently encounter new consumer products and need to process them quickly.
The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape, pose and material properties like friction coefficient or center of mass. 
Furthermore, the robot may not be able to measure these quantities exactly due to sensor noise and missing data resulting from partial visibility and object properties such as transparency, .
Grasp planners that assume exact prior knowledge of object geometry or an exact measurement of pose may fail in this environment.

@@

Grasp quality metrics have been developed to determine if a grasp will be successful or not and how much force it needs to exert to resist an opposing force, however most of them evaluate a grasp assuming all the parameters are known \cite{ferrari1992}.
Recent work motivated using knowledge of uncertainty to select grasps, but most methods for evaluating grasp quality in the presence of uncertainty requires exhaustive sampling over the possible values of the uncertain quantity \cite{kim2012physically, weisz2012pose}.
To select a grasp with high quality this evaluation must be performed for a large set of potential grasps, which can be very time-consuming.
However, when evaluating a set of grasps we may be able to determine the difference of quality between grasps with only a few samples and throw away grasps that are likely to be suboptimal \cite{kehoe2012estimating}.
Thus, we can adaptively concentrate grasp quality evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.

The multi-armed bandit (MAB) model for sequential decision making problems \cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration.
The goal in a MAB model is to make a sequence of decisions over a set of possible options, or ``arms", such that a measure of the expected reward of such decisions is maximized.
Solutions to the MAB model are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model with a finite number of total decisions to be made before a predetermined `stopping time'.
The objective is to maximize the expected reward of the decision made at the stopping time, or equivalently to minimize ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.

Our main contribution in this paper is formulating the problem of planning grasps according to some quality metric in the presence of uncertainty as a budgeted multi-armed bandit model.
We use this formulation to rank a set of potential grasps by the probability of force closure \cite{christopoulos2007handling, kehoe2012toward} under shape uncertainty.
We use a budgeted multi-armed bandit model since we would like to execute only one grasp plan after evaluating the probability of success for many potential grasp plans.
We choose the model of uncertainty to be a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}, but our method applies to any model of uncertainty that can be sampled.

We also show how to estimate distributions on the contact points and surface normals and center of mass using a graphical model to represent uncertainty in motion, shape, pose and friction coefficient. Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of 1000 grasps by 10x, an order of magnitude improvement, over the baseline Monte-Carlo approach. These promising results suggest that our MAB approach could also provide  significant speed improvements using other types of uncertainty, such as pose, friction coefficent or center of mass and provide significant speed improvements. 
\todo{Revise above line, as we now have some experiments varying these quantities as well}

@@

Currently, the most common method of evaluating the expected grasp quality under uncertainty is to rank a set of random grasps on an object using  samples on shapes, pose or parameters to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
Monte-Carlo sampling involves drawing random samples from a distribution to approximate an expected value\cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shapes.

To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo sampling in order to choose the highest quality grasps. The adaptive sampling pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is, which in practice could lead to good grasps being thrown away. 
Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty.
MCMC simplified sampling from a complicated joint distribution on pose and shape, but it can be slow to converge to the correct distribution due to burn in and mixing conditions~\cite{andrieu2003introduction}.

We chose to study our MAB sampling method on distributions for friction coefficient, pose, motion and shape. For shape uncertainty we decided to use a Gaussian process implicit surface representation. Our decision to use this uncertainty model is based on GPIS's ability to combine various modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
Hollinger et al. used GPIS as a model of uncertainty and performed active sensing on the hulls in underwater boats \cite{hollinger2013}.
Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}. However, this relied on an approximation to grasp quality without guarantees on accuracy.. We propose an adaptive sampling approach known as the Multi-Armed Bandit Model.

@@

\subsection{Grasp Metric}
Ferrari and Canny \cite{ferrari1992} demonstrated a method to rank grasps by considering points of contact with an object and the object surface normals at those contacts. The magnitude of the metric allows one to rank grasps by their ability to resist external wrenches (forces and torques) applied to the grasped object. Furthermore, it has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.

The $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$. Then the metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. If the convex hull does enclose the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used. Thus if the hull does not enclose the origin then there exists a wrench that the grasp is not able to resist, which occurs if the quality metric $Q$ is less than zero. A grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$\cite{pokorny2013classical}.

In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps . $P(Q>0)$ may be computed by sampling from our distributions on pose, shape and material properties (friction coefficient) and averaging the qualities that are computed. Reducing the time to find the grasp with the highest probability of force closure from a set of a large number of grasps is the primary focus of the paper.

\subsection{Line of action}
In an uncertain environment may not know the true $g$ exactly due to sensing imprecision. Thus we propose to work with the trajectory of the gripper when analyzing grasps. Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}.
A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.

\subsection{Types of Uncertainty}
In this work we consider the following types of uncertainty shape, pose, movement, and friction coefficient.  The property of force closure is not effected by the center of mass because it only measures if a wrench can be resisted not how large the force is need to resist.  Fig. \ref{fig:graphical_model} shows the probabilistic relationship of all types of uncertainty considered in this work. We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle all types of uncertainty. We note though that our choice of distributions does not effect the performance of the MAB algorithm and the reader should choose distribution that effect their needs.

@@

Shape uncertainty can occur from transparency, occlusions and sensor noise \cite{mahler}. To model this uncertainty we chose to use a Gaussian Process Implicit Surface (GPIS) representation, which is explained in detail in Appendix \ref{sec:Appendix}.  A GPIS is a Gaussian distribution on a signed distance function,$sd$, that describes the workspace. A signed distance function is  greater than 0 outside the surface of an object, 0 at the surface and less than 0 beneath.  The GPIS can be sampled from via $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS. For our application, we set $x$ to discretized points along the workspace $\mathcal{W}$ and for each sample the points that correspond to zero, $sd(x) = 0$, are the contours of the shape. For convenience we will  represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.

@@

 \subsubsection{Distribution on Friction Coefficient}
As shown in \cite{zheng2005}, uncertainty in friction coefficient can play a large role in grasp quality evaluation. The expected friction coefficient $E(\mu)$ can be derived by means of object classification and a look up table. However, because their could be material in between the objects surface and the robot gripper (i.e. dust, water, moisture). It is important to assume noise.  Thus, we purpose sampling the friction coefficient from a Gaussian around the expected friction coefficient $\mu \sim N(E(\mu),\sigma_{\mu}^2)$.

To evaluate the $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig. \ref{fig:graphical_model}. To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$. Using Bayes rule and our graphical model we can rewrite this as

@@

 In Appendix \ref{sec:Appendix}, we look at how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$). Then in Appendix \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and present a novel visualization technique for the distribution on surface normals. Lastly in Appendix \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution.

@@

We assume we are given a 2-D workspace $\mathcal{W}$ with an unknown object represented as a trained GPIS model, described in Section \ref{sec:GP}, and set of possible grasp plans $G$ which are generated either randomly or with a heuristic as in \cite{mahler2015gp}.
We are interested in determining Eq. \ref{eq:problem_def} with respect to a chosen grasp metric Q.

@@

In our setting, we have a probabilistic  representation and would like to evaluate many potential grasps on the samples drawn from the graphical model in Fig. \ref{fig:graphical_model}.
Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.

A common measure of success in MAB problems is {\it regret}, the difference between the expected optimal reward and the expected reward of the selected arm on a single pull.
Traditional bandit algorithms minimize cumulative regret,  the sum of regret over the entire sequence of arm choices. Lai and Robbins showed that an optimal solution to the bandit problem is bounded by a logarithmic function \cite{lai1985asymptotically}. They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically many variants of UCB have thus been purposed. The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest confidence bound.

In the case of grasping, one only cares about the regret when the grasp is actually executed. Hence, the exploration and exploitation stage are decoupled. Our goal is to identify the best arm in as few decisions as possible.
Given a set of arms $\lbrace 1,...K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$ and the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}} \mu_k$.
The simple regret at time $t$ is given by

@@

\subsection{Fixed Budget}
In the Budgeted Multi-Armed Bandit (BMAB) setting the algorithm is given a stopping time and needs to return the best arm at that stopping time. Audibert el al. demonstrated an algorithm called Successive Rejects that divides up the total budget into successively shorter phases and discards the worst arm left at the end of each phase. This algorithm can return the best arm with near-optimal probability depending on the hardness of the problem \cite{audibert2010best}. In addition, UCB-like methods have been proposed that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}. For example in \cite{bubeck2009pure}, they showed a link between simple regret and cumulative regret that allowed for the analysis of the existing bandit algorithms like UCB1.

@@

While, UCB type algorithms adopt a frequenist perspective for distributions with bounded rewards in their empirical estimate of an upper bound. A growing interest though in the MAB community is in bandit algorithms that have Bayesian approach \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}. Here a prior distribution is placed on the distribution to be estimated and utilizing the prior enables a trade off between exploration and exploitation. Empirically Bayesian methods like Thompson sampling have been shown to outperform the UCB family \cite{chapelle2011empirical}.

In the context of grasping, the reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure. This is a Bernoulli distribution which has a conjugate prior known as a Beta distribution. 
Hence, we can now model the distribution on rewards as a Beta-Bernoulli process. Bernoulli distributions are formally the probability $\theta$ that an event has occurred and a Beta distribution is the conjugate prior on the probability of theta or $p(\theta)$. Beta distributions are specified by shape parameters $\alpha$ and $\beta$, to update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$. The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.

Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on center of pose $P (\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$. The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$. Thus, we can write the expected probability of force closure as follows

@@

Where $Q(\Gamma|\theta,\xi,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(\theta)$,$p(\xi)$,$p(\rho)$ and $p(\mu)$. Whats interesting in the context of a Bayesian BMAB problem our complicated graphical model in Fig. \ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality. It is this intuition that helps explain the performance of the BMAB algorithms.

@@

\subsection{Thompson Sampling}
Thompson Sampling is a Bayesian method for the multi-armed bandit problem. The main idea behind it is to update the conjugate prior for the distribution of the arm recently pulled, then sample from the prior distribution on all arms and pull the arm with the highest sample drawn. The full algorithm is shown in Algorithm 1.  Empirically this method has been shown to outperform frequentist methods like UCB in certain settings \cite{chapelle2011empirical}

\begin{algorithm}
 \KwResult{Best Arm, $g^*$ }
 For Beta(1,1) prior: \\
\For{ t=1,2,...}{ 
 Draw $p_{j,t} \sim$ Beta($S_{j,t}+1$,$F_{j,t}+1$) for $j = 1,...,k$\\
 Play $I_t=j$ for $j$ with maximum $p_{j,t}$\\
 Observe reward $X_{I_t,t} \in \lbrace 0,1 \rbrace$\\
 Update posterior:\\
 Set $S_{I_t,t+1} = S_{I_t,t} + X_{I_t,t}$ \\
 Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\

>>>>

\title{\LARGE \bf
Efficient Planar Sample-Based Grasp Planning with Uncertainty Using Budgeted Multi-Armed Bandit Models for  [v3 Jan 5, 2015 ] }

@@

\begin{abstract}
\textit{Note to Practitioners---}Planning for a grasp in an unknown environment can be difficult due to uncertainties. For example, a given object may have transparency which makes modern kinect-like sensor unable to accurately determine shape or an object may have a built up of mildew or dust, which makes the friction coefficient unknown. To handle all the uncertainties and plan for grasps using a grasp metric, one must perform monte-carlo integration and exhaustively evaluate samples. We show that by using simple algorithms from the Multi-Armed bandit literature, you can intelligently decided which grasp to sample from next and quickly determine the best grasp in a given set of proposed grasps, thus helping to alleviate the computational burden that is associated to incorporating uncertainty. 
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Consider a robot processing orders in a warehouse , where it frequently encounter new consumer products and need to process them quickly.
The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape, pose and material properties like friction coefficient or center of mass. 
Furthermore, the robot may not be able to measure these quantities exactly due to sensor noise and missing data resulting from occlusions and object properties such as transparency or reflective surfaces .

@@

Grasp quality metrics have been developed to determine if a grasp will be successful or not prior to actually executing the grasp and how much force it needs to exert to resist an opposing force, however the ones that we consider evaluate a grasp assuming all the parameters are known \cite{ferrari1992}.
Recent work \cite{kehoe2012estimating,mahler2015gp} motivated using knowledge of uncertainty to select grasps, but most methods for evaluating grasp quality in the presence of uncertainty use Monte Carlo sampling over the possible values of the uncertain quantity \cite{kim2012physically, weisz2012pose}.

To select a grasp with high quality this evaluation is usually performed for a large set of perturbations in state, shape, and material properties, which can be very time-consuming.
However, when evaluating a set of grasps we may be able to determine the difference of quality between proposed grasps with only a few samples and adaptively choose what grasp to evaluate next. We can concentrate grasp quality evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.

The multi-armed bandit (MAB) model for sequential decision making problems \cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a way to reason about selecting the next option to evaluate.
The goal in a MAB model is to make a sequence of decisions over a set of possible options, or ``arms", such that a measure of expected reward is maximized.
Solutions to the MAB model are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model where at a given "stopping time" the agent must choose the arm that currently has the highest expected reward based on its observations. 
The objective is to maximize the expected reward of the decision made at the stopping time, or equivalently to minimize ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.

Our main contribution is formulating the problem of planning grasps according to some quality metric in the presence of uncertainty as a budgeted multi-armed bandit model.
We use this formulation to rank a set of potential grasps by the probability of force closure \cite{christopoulos2007handling, kehoe2012toward} under uncertainty in pose, shape, motion and friction coefficient. 
We choose the model of shape uncertainty to be a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}.  Uncertainty in pose is represented as a normal distributions around the orientation and translation of the object. Uncertainity in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.  Our approach of treating grasp selection as a BMAB requires only the ability to sample from a given representation of uncertainty and is not restricted to aforementioned representations.

We also show how to estimate distributions on the contact points and surface normals and center of mass using GPIS representation for shape uncertainty. Our experiments demonstrate that using the MAB sampling method improves the time to find the best grasp in a set of 1000 grasps by 5x over the baseline Monte-Carlo approach. 
\todo{Going to get a table with results}

@@

One method of evaluating the expected grasp quality under uncertainty is to rank a set of random grasps on an object using  samples on shapes, pose or parameters to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
Monte-Carlo sampling involves drawing random samples from a distribution to approximate an expected value\cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shapes.

To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of samples needed in Monte-Carlo sampling to choose the highest quality grasps. However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is, which in practice could lead to good grasps being thrown away.
Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty when the robot is able to obtain new information via tactile sensor.
MCMC provides a Bayesian framework for inference with a hidden state, but it can be slow to converge to the correct distribution due to burn in and mixing conditions~\cite{andrieu2003introduction}.

We chose to study our MAB sampling method on distributions for friction coefficient, pose, motion and shape. For shape uncertainty we decided to use a Gaussian process implicit surface representation. Our decision to use this uncertainty model is based on GPIS's ability to combine different modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
Hollinger et al. used GPIS as a model of uncertainty to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.  However, this relied on an approximation to grasp quality without guarantees on accuracy. We propose an adaptive sampling approach known as the Multi-Armed Bandit Model. This paper is a substantially revised and expanded version on \cite{laskey} and \cite{mahler2015gp}.

@@

\subsection{Grasp Metric}
Ferrari and Canny \cite{ferrari1992} demonstrated a method to rank grasps by considering points of contact with an object and the object surface normals at those contacts. The magnitude of the metric allows one to rank grasps by their ability to resist external wrenches (forces and torques) applied to the grasped object. The Ferrari-Canny metric has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.

Let Q be the $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$. The metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. If the convex hull  encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used. A grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$\cite{pokorny2013classical}.

In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps . $P(Q>0)$ may be computed by sampling from distributions on pose (rotation and translation of the object), shape and material properties (friction coefficient) and averaging the qualities that are computed.

\subsection{Line of action}
In an uncertain environment, a grasp planner may not know the true grasp parameters or $g$ exactly due to sensing imprecision. Thus we propose to work with the trajectory of the gripper when analyzing grasps. Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}.
A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.

\subsection{Types of Uncertainty}
In this work we consider the following types of uncertainty shape, pose, movement, and friction coefficient.  The property of force closure is not affected by the center of mass because it  measures if a wrench can be resisted not how large the force is need to resist.  Fig. \ref{fig:graphical_model} shows the probabilistic relationship of the types of uncertainty considered in this work. We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle the types of uncertainty. We note though that our choice of distributions does not effect the ability to use the MAB algorithms and that the reader should choose distribution that effect their needs.

@@

Shape uncertainty can occur from transparency, occlusions and sensor noise \cite{mahler}. To model this uncertainty we use a Gaussian Process Implicit Surface (GPIS) representation, which is explained in detail in Appendix \ref{sec:Appendix}.  A GPIS is a Gaussian distribution on a signed distance function,$sd$, that describes the workspace. A signed distance function is  greater than 0 outside the surface of an object, 0 at the surface and less than 0 beneath.  Signed distance functions can be sampled from  $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS. For our application, we set $x$ to discretized points along the workspace $\mathcal{W}$ and for each sample the points that correspond to zero, $sd(x) = 0$, are the contours of the shape. For convenience we will  represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.

@@

 \subsubsection{Distribution on Friction Coefficient}
As shown in \cite{zheng2005}, uncertainty in friction coefficient can play a large role in grasp quality evaluation. The expected friction coefficient $E(\mu)$ can be derived by means of object classification and a look up table. However, because their could be material in between the objects surface and the robot gripper (i.e. dust, water, moisture), we purpose sampling the friction coefficient from a Gaussian around the expected friction coefficient $\mu \sim N(E(\mu),\sigma_{\mu}^2)$.

To estimate $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig. \ref{fig:graphical_model}. To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$. Using Bayes rule  we can rewrite this as

@@

 Appendix \ref{sec:Appendix}, describes how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$). Appendix \ref{sec:normals}, describes how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and presents a novel visualization technique for the distribution on surface normals.  Appendix \ref{sec:mass}, describes a way to calculate the expected center of mass assuming a uniform mass distribution.

@@

We assume we are given a 2-D workspace $\mathcal{W}$ with an unknown object represented as a trained GPIS model, described in Section \ref{sec:GP}, and set of possible grasp plans $G$ which are generated either uniformly randomly or with a heuristic as in \cite{mahler2015gp}.
We are interested in determining Eq. \ref{eq:problem_def} with respect to the problaliltiy of achieving force closure or $P(Q(\Gamma) > 0)$. \todo{Need to figure out if we can use optimal or not}

@@

In our setting, we have a probabilistic  representation and would like to evaluate many potential grasps on the samples drawn from the graphical model in Fig. \ref{fig:graphical_model}.
Motivated by limited computational resources we  allocate sampling resources to efficiently find the best arm.
Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.

A common measure of success in MAB problems is {\it regret}, the difference between the expected optimal reward and the expected reward of the selected arm on a single pull.
Traditional bandit algorithms minimize cumulative regret,  the sum of regret over the entire sequence of arm choices. Lai and Robbins showed that an optimal solution to the bandit problem is bounded by a logarithmic function \cite{lai1985asymptotically}. They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically. Many variants of UCB have thus been proposed. The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.

In the context of finding a high quality grasp, one only cares about the regret when the grasp is actually executed in real life. The agent shouldn't be penalized for exploring different grasps, but only for the grasp that they suggest at the termination of the algorithm. Hence, the exploration and exploitation stage are decoupled. Our goal is to identify the best arm in as few decisions as possible.
Given a set of arms $\lbrace 1,...K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$ and the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}} \mu_k$.
The simple regret at time $t$ is given by

@@

The speed of termination is affected by the hardness of the problem, which relates to the how close the other arms expected reward is to the expected reward top arm in the set \cite{audibert2010best}. In the grasping context this means that achieving a fixed confidence for two similar grasps would require exhaustive sampling from each distribution.

\subsection{Fixed Budget}

In the Budgeted Multi-Armed Bandit (BMAB) setting the algorithm is given a stopping time and needs to return the current best arm at that stopping time this can be thought of as an anytime algorithm.   Audibert el al. demonstrated an algorithm called Successive Rejects that divides up the total budget into successively shorter phases and discards the worst arm left at the end of each phase. This algorithm can return the best arm with near-optimal probability depending on the hardness of the problem \cite{audibert2010best}. In addition, UCB-like methods have been proposed that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}. For example in \cite{bubeck2009pure}, they showed a link between simple regret and cumulative regret that allowed for the analysis of the existing bandit algorithms like UCB1.

@@

While, UCB type algorithms adopt a frequenist perspective for distributions with bounded rewards in their empirical estimate of an upper bound. A growing interest though in the MAB community is in bandit algorithms that have Bayesian approach \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}. Here a prior distribution is placed on the distribution to be estimated and utilizing the prior enables a trade off between exploration and exploitation. Theoretical results have shown that these methods are capable of achieving the lower bound described by Lai and Robbin \cite{agrawal2011analysis} \cite{kaufmann2012bayesian}. Furthermore in an empirical study Bayesian methods have been shown to outperform the UCB family \cite{chapelle2011empirical}.

In the context of grasping, the reward from sampling from the grasp distribution is 1 if the sampled grasp is in force closure and 0 if the grasp is not in force closure. The distribution that describes whether an event is $\lbrace 0, 1 \rbrace$ is known as a Bernoulli distribution and can be described by the parameter $\theta$ or the probability an event occurs. In the Bayesian setting one would treat $\theta$ as belonging to a distribution. A convenient and common choice for such a distribution is the Beta distribution. Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where ($\alpha >0$ and $\beta >0$). The mean of the Beta distribution is given by $\alpha/(\alpha+\beta)$. To update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$. The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.

Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on pose $P (\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$. The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$. Thus, we can write the expected probability of force closure as follows

@@

Where $Q(\Gamma|\theta,\xi,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(\theta)$,$p(\xi)$,$p(\rho)$ and $p(\mu)$. Whats interesting in the context of a Bayesian BMAB problem our  graphical model in Fig. \ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality. Regardless of the distributions in Fig. \ref{fig:graphical_model}, we are still able to maintain the theoretical guarantees given by the Bayesian MAB algorithms because the probability of force closure is a Beta-Bernoulli Process \cite{agrawal2011analysis} \cite{kaufmann2012bayesian} \cite{weber1992gittins}.

@@

\subsection{Bayes-UCB}
Bayes UCB, detailed in Algorithm 1, is a version of the UCB algorithm that uses a Bayesian posterior update to get a confidence bound instead of  the frequentist concentration inequality approach. To get an upper confidence bound from the posterior, the Bayes UCB algorithm uses the quantile of the Beta distribution up to a specified probability which depends on the timestep and horizon. TAt each time step the arm with the highest quantile is chosen and the Beta distribution is updated based on the observed reward.  For binary rewards (i.e. Bernoulli distributions) the expected number of pulls of suboptimal arms is bounded and experimentally this algorithm has been shown to outperform UCB for binary rewards \cite{kaufmann2012bayesian}.

\begin{algorithm}
 \KwResult{Current Best Arm, $\Gamma^*$ }
 For Beta(1,1) prior, Stopping Horizon $n$: \\
\For{ t=1,2,...,n}{ 
	\For{j = 1,...,K}{
